---
title: "TruckLoad Cost Health Report"
output:
   flexdashboard::flex_dashboard:
    #orientation: rows
    source_code: embed
    logo: T:/SalesAndOps/Sales and Ops Planning/Large Parcel/Forecasting/Dashboards/Actuals/Wayfair-Logo-US-New.png
---

<style>
.navbar {
  background-color:#377586;
}
.section.sidebar {
  top: 61px;
  border-bottom: 10px solid #ececec;
  border-left: 10px solid #ececec;
  background-color: rgba(255, 255, 255, 1);
}
</style>

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(RODBC)
library(lubridate)
library(plotly)
library(reshape2)
library(stringr)

source('T:/SalesAndOps/Transportation/Transportation Finance/z. Personal Folder/Yin Z/CostHealth/costhealth.R')
ServiceType = 'TL'
```

High Level Summay
=====================================

Column {data-width=650}
-------------------------------------

### WoW Var Summary

```{r}
ggplot(InvoiceLevelPlot %>% filter(TMSServiceCode == ServiceType),aes(x = InvoiceWeek)) +
  geom_bar(data = bardata %>% filter(TMSServiceCode == ServiceType), aes(y = value,fill = variable),stat="identity", position=position_dodge()) +

  geom_line(data = linedata%>% filter(TMSServiceCode == ServiceType), aes(y = value * 3000,group = variable,color = variable),size= 1, linetype = 'dashed') +
  geom_point(data = linedata%>% filter(TMSServiceCode == ServiceType), aes(y = value * 3000,group = variable,color = variable),size= 1.5) +
  scale_y_continuous(
    name = "Variance ($)",
    sec.axis = sec_axis(~./3000, name = "Variance (%)")
  ) +
  geom_text(data = linedata %>% filter(TMSServiceCode == ServiceType), aes(label = paste0(round(value,1), '%'),
                                 y = value * 3000, group = variable),size = 3.2, vjust=0,check_overlap = TRUE) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(color = 'black', size=10),
    axis.title.y.right = element_text(color = 'black', size=10),
    plot.title = element_text(size = 10, face = "bold"),
    legend.position="top",
    legend.title = element_blank(),
    legend.text = element_text(size = 8)

  ) +
  scale_fill_brewer(palette="Blues") +
  
  #facet_wrap(~TMSServiceCode) +
  ggtitle('WoW Cost Variance')

```

Column {data-width=350}
-------------------------------------
### WoW Rated/Invoice Var BreakDown $

```{r}

ggplotly(
  ggplot(data = bardata_item %>% filter(TMSServiceCode == ServiceType), aes(x = InvoiceWeek, y = value,fill = variable)) +
    geom_bar(stat="identity", position=position_dodge()) +
    ylab('Var ($)') +
    #scale_fill_brewer(palette="Spectral") +
    scale_fill_manual(values=c("#D53E4F", "#FDAE61", "#ABDDA4","#3288BD")) +
    theme_minimal() +
    theme(legend.position="top",
    legend.title = element_blank(),
    legend.text = element_text(size = 6))
    #facet_wrap(~TMSServiceCode) +
    #ggtitle('WoW Cost Variance Breakdown')
) %>%
  layout(legend = list(orientation = "h"))
```

### WoW Rated/Invoice Var BreakDown %

```{r}

myplot = ggplotly(
  ggplot(linedata_item %>% filter(TMSServiceCode == ServiceType) %>% select(-c('TMSServiceCode')),
         aes(x = InvoiceWeek,y = value,group = variable,color = variable,text = sprintf('Var:%.2f%%  Type: %s',value,variable))) +

    geom_line(linetype = 'dashed') +
    geom_point() +
    ylab('Var (%)') +
    #scale_fill_brewer(palette="Spectral") +
    scale_color_manual(values=c("#D53E4F", "#FDAE61", "#ABDDA4","#3288BD")) +
    ylim(-50,30) + 
    theme_minimal() +
        theme(legend.position="top",
    legend.title = element_blank(),
    legend.text = element_text(size = 6))
    #facet_wrap(~TMSServiceCode) +
    #ggtitle('WoW Cost Variance Breakdown')
, tooltip = c('x','text')) %>%
  layout(legend = list(orientation = "h"))

for (i in 1:length(myplot$x$data)){
  if (!is.null(myplot$x$data[[i]]$name)){
    myplot$x$data[[i]]$name =  gsub("\\(","",str_split(myplot$x$data[[i]]$name,",")[[1]][1])
  }
}

myplot
```


Unplanned ACC
=====================================
Column {data-width=500}
-------------------------------------
```{r}
ggplotly(
  ggplot(data = bardata_item_UnplannedACC %>% filter(TMSServiceCode == ServiceType), aes(x = InvoiceWeek, y = value,fill = variable)) +
    geom_bar(stat="identity", position=position_dodge()) +
    ylab('Var ($)') +
    #scale_fill_brewer(palette="Spectral") +
    scale_fill_manual(values=c("#D53E4F", "#FDAE61", "#ABDDA4","#3288BD")) +
    theme_minimal() +
    theme(#legend.position="bottom",
    legend.title = element_blank(),
    legend.text = element_text(size = 6))
    #facet_wrap(~TMSServiceCode) +
    #ggtitle('WoW Cost Variance Breakdown')
) %>%
  layout(legend = list(orientation = "h",x=0,y=1))

```



Column {data-width=500}
-------------------------------------
```{r}
myplot = ggplotly(
  ggplot(linedata_item_UnplannedACC %>% filter(TMSServiceCode == ServiceType) %>% select(-c('TMSServiceCode')),
         aes(x = InvoiceWeek,y = value,group = variable,color = variable,text = sprintf('Var:%.2f%%  Type: %s',value,variable))) +

    geom_line(linetype = 'dashed') +
    geom_point() +
    ylab('Var (%)') +
    #scale_fill_brewer(palette="Spectral") +
    scale_color_manual(values=c("#D53E4F", "#FDAE61", "#ABDDA4","#3288BD")) +
    #ylim(-50,30) + 
    theme_minimal() +
        theme(#legend.position="bottom",
    legend.title = element_blank(),
    legend.text = element_text(size = 6))
    #facet_wrap(~TMSServiceCode) +
    #ggtitle('WoW Cost Variance Breakdown')
, tooltip = c('x','text')) %>%
  layout(legend = list(orientation = "h", x = 0, y = 1))

for (i in 1:length(myplot$x$data)){
  if (!is.null(myplot$x$data[[i]]$name)){
    myplot$x$data[[i]]$name =  gsub("\\(","",str_split(myplot$x$data[[i]]$name,",")[[1]][1])
  }
}

myplot
```

Spot Rate
=====================================
Column {data-width=500}
-------------------------------------
### chart1
```{r}
ggplotly(ggplot(weeklyspotratetruck, aes(x = InvoiceWeek)) +
           geom_bar(aes(y = TruckCount),stat="identity",fill = "#66CC99") +
           ggtitle('Matched Spot Rate Truck')) %>%
  layout(legend = list(orientation = "h", x = 0, y = 1))
```

### chart2
```{r}
ggplotly(ggplot(weeklyspotratetruck %>%
                  select(InvoiceYear,InvoiceWeek,SpotTtlCost, LiTtlCost, LiTtlRatedCost) %>%
                  melt(., id.vars = c('InvoiceYear','InvoiceWeek')),
                aes(x = InvoiceWeek, y = value, group = variable,fill = variable)) +
           geom_bar(stat="identity",position=position_dodge()) +
           ggtitle('Cost Comparison'))
```




Column {data-width=500}
-------------------------------------
### chart3
```{r}
ggplotly(ggplot(weeklyspotratetruck %>% 
                  select(InvoiceYear,InvoiceWeek,`Spot/Invoice Var$`,`Rated/Invoice Var$`) %>%
                  melt(., id.vars = c('InvoiceYear','InvoiceWeek')), 
                aes(x = InvoiceWeek, y = value, group = variable,fill = variable)) +
           geom_bar(stat="identity",position=position_dodge()) +
           ggtitle('Cost Variance $')) %>%
  layout(legend = list(orientation = "h", x = 0, y = 1))
```
           

### chart4
```{r}
ggplotly(ggplot(weeklyspotratetruck %>% 
                  select(InvoiceYear,InvoiceWeek,`Spot/Invoice Var%`,`Rated/Invoice Var%`) %>%
                  melt(., id.vars = c('InvoiceYear','InvoiceWeek')), 
                aes(x = InvoiceWeek, y = value, group = variable,color = variable)) +
           geom_point() +
           geom_line() +
           ggtitle('Cost Variance %')) %>%
  layout(legend = list(orientation = "h", x = 0, y = 1))
```




Truckload Matching
=====================================
Column {data-width=500}
-------------------------------------
```{r}
ggplotly(ggplot(truckmatchplot %>%
                  filter(InvoiceWeek %in% hist_week),
                aes(x = InvoiceWeek, y = InvoiceCount, group = IN_Ex_Issue, color = IN_Ex_Issue)) +
           geom_point() +
           geom_line(linetype = 'dashed') +
           ylab('Invoice Count') +
           ggtitle('Invoice with Truck Matching Issue')) %>%
  layout(legend = list( x = 0, y = 1))
```
           

Column {data-width=500}
-------------------------------------
```{r}
ggplotly(ggplot(currenthelptruckmatchplot,
                aes(x = IN_Ex_Issue, y = InvoiceCount, group = IssueString, fill = IssueString)) +
           geom_bar(stat="identity") +
           ylab('Invoice Count') +
           ggtitle('Current Help Status Invoice with Truck Matching Issue')) %>%
  layout(legend = list(x = 0, y = -2))

```



  
Success Metrics
=====================================
Row
-------------------------------------
    
### Chart 1
    
```{r}
ggplotly(ggplot(rateplotdata %>% 
                  melt(., id.vars = c('InvoiceWeek'), 
                       measure.vars = c('AutoMatchingRate','AutoApproveRate','ReProcessRate')),
                aes(x = InvoiceWeek, y = value, group = variable, color = variable)) +
           geom_point() +
           geom_line(linetype = 'dashed') +
           ylab('Rate') +
           ggtitle('Success Metrics'))
```
 
### Chart 2
    
```{r}
ggplotly(ggplot(rateplotdata %>% 
                  select(NonActiveHelp, InvoiceWeek,`Active Help`) %>%
                  melt(., id.vars = c('InvoiceWeek')),
                aes(x = InvoiceWeek, y = value, group = variable, fill = variable)) +
           geom_bar(stat="identity") +
           ylab('Invoice Count') +
           ggtitle('Invoice Count by Week'))
``` 

Row
-------------------------------------
    
### Chart 3
    
```{r}
ggplotly(ggplot(snapshot %>% filter(CurrentStatus %in% c('Complete','Help','Disputed')) %>%
                  mutate(pct = paste0(round(InvoiceCount / sum(InvoiceCount) * 100,1),'%')),
                aes(x = CurrentStatus, y = InvoiceCount, group = Status, fill = Status)) +
           geom_bar(stat = 'identity') +
           geom_text(aes(label = pct,
           y = InvoiceCount, group = Status),size = 3.2, vjust=0) +
           ggtitle('Invoice Current Status (past 180 days)'))     
```
    
### Chart 4

```{r}
ggplotly(ggplot(disputeplotdata,
                aes(x = DisputeResult, y = InvoiceCount, group = Status, fill = Status)) +
           geom_bar(stat = 'identity') +
           # geom_text(aes(label = pct,
           #               y = InvoiceCount, group = Status),size = 3.2, vjust=0) +
           theme(axis.text.x = element_text(angle = 30), text = element_text(size=10)) +
           ggtitle('Dispute Invoice Aging (past 180 days)'))
```
                      
